Xor-Some Preregistered Study: Preprocessing

### 2022-05-10 analysis/main/01_xor-some_prereg_preprocessing_final.Rmd
replicate MFs prior-means-first analysis

@@

>>>>

# perform the conceptually cleaner procedure: average over prior ratings first, then z-score
d_critical_zScored_noDuplicates %>% unique() %>% 
  select(submission_id, title, main_type, block_extended, response) %>%
  pivot_wider(
    names_from = block_extended, 
    values_from = response, 
    values_fn = mean # getting means for double prior measurement in "xor"
  ) %>%
  pivot_longer(
    cols=c(relevance, competence, prior, target),
    names_to = "block_extended",
    values_to = "response"
  ) -> d_critical_zScored_meanFirst_noDupl

d_critical_zScored_meanFirst_noDupl_zScored <- d_critical_zScored_meanFirst_noDupl %>%  
  group_by(submission_id, block_extended) %>%
  mutate(block_mean = mean(response),
         block_sd = sd(response),
         response_centered = (response - block_mean)/block_sd,
         # catch the cases where sd is 0 
         response_centered = ifelse(is.na(response_centered), 0, response_centered))

d_critical_zScored_meanFirst_noDupl_zScored_wide <- d_critical_zScored_meanFirst_noDupl_zScored %>% 
  select(submission_id, title, main_type, block_extended, response_centered) %>% 
  unique() %>% 
  pivot_wider(
    names_from = block_extended, 
    values_from = response_centered, 
    values_fn = mean # getting means for double prior measurement in "xor"
  )

@@

d_critical_zScored_meanFirst_noDupl_zScored %>%
  write_csv("./../../data/main/results_prereg_tidy_noDuplicates_zScored_meansFirst_long.csv")
d_critical_zScored_meanFirst_noDupl_zScored_wide %>%
  write_csv("./../../data/main/results_prereg_tidy_noDuplicates_zScored_meansFirst_wide.csv")
```
